A Grimm idea

### 2016-05-02 presentation/main.tex
worked on presentation

\usepackage[utf8]{inputenc}
\usepackage{epigraph}

\usetheme{metropolis}

@@

\begin{document}
\maketitle
\begin{frame}
  \frametitle{}
  \epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
    Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten %
  wie neu geschlagene Batzen und zeigten ihnen den Weg.}%
  {\emph{Hänsel und Gretel}\\Brüder Grimm}
\end{frame}
\end{document}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{epigraph}
\usepackage{tikz}

\input{tikz/settings}

\usetheme{metropolis}
\metroset{numbering=fraction}

@@

\begin{document}
\maketitle
\begin{frame}
  \frametitle{Motivation}
  \begin{itemize}
    \item Traversing Brobdingnagian graphs
    \item[$\rightarrow$] Web crawlers
    \item Agent moves over vertices along edges
    \item[$\Rightarrow$] Memory efficient agents
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Agents}
  \begin{quotation}
    Und als der volle Mond aufgestiegen war, so nahm Hänsel sein
    Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten
    wie neu geschlagene Batzen und zeigten ihnen den Weg.
  \end{quotation}
  \vspace{-0.5cm}
  \flushright{Brüder Grimm}
  \vspace{-0.5cm}
  \flushright{\emph{Hänsel und Gretel}}
  \begin{itemize}
    \item Agent carries set of markers $\rightarrow$ pebbles
    \item Leave pebbles on vertices
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Brobdignagian graphs}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Indistinguishable vertices
      \item Bounded degree ($\Delta$)
      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$ (Port)
      \item Agent is aware of:
        \begin{enumerate}
          \item Degree  of vertex
          \item Pebbles placed on vertex
          \item Pebbles carried by agent
          \item Port    agent entered vertex
        \end{enumerate}
    \end{itemize}
    \column{0.5\textwidth}
    \begin{center}
      \resizebox{\textwidth}{!}{\input{tikz/portex}}
    \end{center}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Exploration sequence}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Describe movement of agent by relative turns
      \item $e_{1},\dots, e_{n}$
      \item For a vertex $v$ with degree $d_{v}$ which is entered on port $p$
        is left through port $p + e_{i}\mod p$
      \item<2->[$\rightarrow$] Example:
        $\only<3-3>{\colorbox{green}}{1}\;,\only<4-4>{\colorbox{green}}{3}\;,
        \only<5-5>{\colorbox{green}}{2}\;,\only<6-6>{\colorbox{green}}{2}$
    \end{itemize}
    \column{0.5\textwidth}
    \begin{center}
      \resizebox{\textwidth}{!}{\input{tikz/moveex}}
    \end{center}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{}
\end{frame}
\end{document}
